Evolution of ORM Systems: Formal Foundations

### 2013-01-17 doc/description.tex
fixed formating of alterTable

\paragraph{Alter Table} The $alterTable$ function renames a table in  the database.
\begin{align*}
alterTable:  Label \times Label \times Database \rightarrow Database \\
alterTable(l_o, l_n, d) = \inference{\exists t \in tables(d) : name(d) = l_o \\ \wedge \forall e \in tables(d) : name(e) \neq l_n}{\begin{gathered}
t.name = l_n \\ \wedge \forall e \in tables(a) \wedge \forall (f \in fks(e) \wedge reference(f) = l_o ) \\ : f.reference = l_n 
\end{gathered}}\\
l_o, l_n \in Label, s \in States, a \lhd Applications, d \lhd Database
\end{align*}

>>>>

\paragraph{Alter Table} The $alterTable$ function renames a table in  the database.
\begin{align*}
	\mathbf{alterTable} : Label \times Label \times Database \rightarrow Database \\
	alterTable(l_o, l_n, d) = \inference{\exists t \in tables(d) : name(d) = l_o \\ \wedge \forall e \in tables(d) : name(e) \neq l_n}{\begin{gathered}
		t.name = l_n \\ \wedge \forall e \in tables(a) \wedge \forall (f \in fks(e) \wedge reference(f) = l_o ) \\ : f.reference = l_n 
	\end{gathered}}\\
	l_o, l_n \in Label, s \in States, a \lhd Applications, d \lhd Database
\end{align*}
